---
title: "Bayesian Portfolio Posterior Return and Risk"
---

For stocks, the stock returns are assumed to be normally distributed with a mean return vector and a covariance matrix. A portfolio is simply a weight vector tells us to allocate assets. Portfolio return is a weighted sum, portfolio risk is a quadratic form. 

From the assumption, we can obtain posterior mean return vectors and posterior covariance matrices for the stock returns. 

```{r}
#| warning: false
rm(list=ls(all=TRUE))

library(ggplot2)
library(dplyr)
library(rjags)
library(tidybayes)
library(xts)
library(SharpeR)# data

data(stock_returns)
r<-stock_returns
head(r)
N=nrow(r)
K=4
set.seed(123)

model_code <- "
model {
  #likelihood
  for (i in 1:N) {
    y[i,] ~ dmnorm(mu, Sigma_Inv)
  }

  # Prior on mean vector
  for(k in 1:K) {
    mu[k]~dnorm(0, 1 /100 ^ 2)
  }

  # Prior on covariance matrix
  Sigma_Inv ~ dwish(I, K+1)
}
"
data_list <- list(
  N = N,
  K=K,
  I = diag(K),
  y=r
)
model <- jags.model(textConnection(model_code), 
                    data=data_list, 
                    n.chains = 5);
update(model, 1000, progress.bar = "none"); # Burnin for 1000 samples

posterior_sample <- coda.samples(model, 
                                 variable.names = c("mu","Sigma_Inv"),
                                 n.iter = 10, progress.bar = "none")

#summary(posterior_sample)

mu_dat <-         posterior_sample %>% spread_draws(mu[i]|i)#tidybayes
Sigma_Inv_dat <- posterior_sample %>%  tidy_draws(Sigma_Inv)#tidybayes
```
With a known portfolio vector, the posterior portfolio return @fig-posterior-portfolio-return  is a weighted sum of posterior stock mean returns. The posterior portfolio risk @fig-posterior-portfolio-risk is a quadratic form of posterior return covariance matrices.
```{r}
#| label: fig-posterior-portfolio-return
#| fig-cap: "Posterior Portfolio Return Distribution"
#| warning: false
#portfolio return posterior distribution
port=c(0.20247656,  0.26518714, 0.3566089,  0.17572744)

er=as.matrix(mu_dat[,4:7])
port.return=er%*%port
plot(density(port.return),lwd=4,col=4,main="Porsterior Return Distribution")
```

```{r}
#| label: fig-posterior-portfolio-risk
#| fig-cap: "Posterior Portfolio Risk Distribution"
#| warning: false
#portfolio risk posterior distribution
port.risk=NULL
for(i in 1:nrow(Sigma_Inv_dat)){
  covmat = solve(matrix(as.numeric(Sigma_Inv_dat[i,4:19]),ncol=4))
  port.risk=c(port.risk,port%*%covmat%*%port)
}
plot(density(port.risk),lwd=4,col=4,main="Posterior Risk Distribution")

```
