---
title: "Bayesian Posterior Portfolio Frontier"
---

It was in our financial theory classes, we were introduced to portfolio frontier and optimized portfolio, especially the minimum risk portfolio. But when we applied the theory from class the minimum risk portfolio was not minimum risk at all. 

Think about it in the real world, every time we want to do something a new set of data are deliver to us. Only look at one set of data or one frontier is insufficient. Luckily rJAGS can help us to simulate the full set of posterior distribution of frontiers. We can have an overall view of the portfolio optimization problem. 

We first load the data, and compute the direct estimated portfolio frontier.
```{r}
#| warning: false
rm(list=ls(all=TRUE))

library(ggplot2)
library(dplyr)
library(rjags)
library(tidybayes)
library(IntroCompFinR )
library(xts)
library(SharpeR)# data

data(stock_returns)
r<-stock_returns
head(r)
N=nrow(r)
K=4
set.seed(123)

#Direct estimation
Er=colMeans(r)
S=cov(r)

ef <- efficient.frontier(Er, S, alpha.min=-2,
                         alpha.max=1.5, nport=20)
y= ef$er
x= ef$sd
```

We generate posterior distribution of returns and covariance matrix.
```{r}

model_code <- "
model {
  #likelihood
  for (i in 1:N) {
    y[i,] ~ dmnorm(mu, Sigma_Inv)
  }
  for(k in 1:K) {
    mu[k]~dnorm(0, 1 /100 ^ 2)
  }

  # Prior on covariance matrix
  Sigma_Inv ~ dwish(I, K+1)
}
"
data_list <- list(
  N = N,
  K=K,
  I = diag(K),
  y=r
)
model <- jags.model(textConnection(model_code), 
                    data=data_list, 
                    n.chains = 5);
update(model, 1000, progress.bar = "none"); # Burnin for 1000 samples

posterior_sample <- coda.samples(model, 
                                 variable.names = c("mu","Sigma_Inv"),
                                 n.iter = 10, progress.bar = "none")

#summary(posterior_sample)

mu_dat <-         posterior_sample %>% spread_draws(mu[i]|i)#tidybayes
Sigma_Inv_dat <- posterior_sample %>%  tidy_draws(Sigma_Inv)#tidybayes
```

Construct all frontiers from the posterior distribution. 
```{r}
#Posterior frontiers
efr=NULL
efs=NULL
n=nrow(mu_dat)
m=20
for(i in 1:n){
  er =as.numeric(mu_dat[i,4:7])
  covmat = solve(matrix(as.numeric(Sigma_Inv_dat[i,4:19]),ncol=4))

  # compute portfolio frontier
  ef <- efficient.frontier(er, covmat, alpha.min=-2,
                         alpha.max=1.5, nport=m)
 efr=c(efr, ef$er)
 efs=c(efs, ef$sd)
}
```

Plot the posterior frontiers.
```{r}
#| label: fig-frontier
#| fig-cap: "Posterior frontier Distribution"
#| warning: false
ggplot() +
  # Plot posterior sample densities
  geom_path(
    aes(x = efs, y = efr,group = rep(1:n, each = m),linetype = "Posterior frontiers" ),
    color = "gray",
    alpha = 0.5
  ) +
 
  # Plot posterior expected density
  geom_path(
    aes(x = x, y =y,linetype = "Direct estimated frontier" ),
    color = "black"
  ) + labs(linetype ="")+ #"Reference Lines"

  # Labels and theme
  labs(
    x = "Risk",
    y = "Expected Return"
  )+theme(legend.position = "top")

```
@fig-frontier The minimum risk portfolio from direct estimation (black curve) has daily return around 0.00025. But our posterior frontiers show that many minimum risk portfolios have daily return less than 0.00025 or lower than zero. We cannot reject Hypothesis that minimum risk portfolio return is less than 0. 
