---
title: "Black-Litterman Posterior Predictive"
---
Say there are 4 stocks, their daily returns are assumed to be normally distributed with means and a covariance matrix. If someone tell us, there was one day the stocks had a portfolio gained such such return. Should we believe it?

Let's say the portfolio was $(0.20247656,  0.26518714, 0.3566089,  0.17572744)$,  and the portfolio return on that day was $0.01016$. Black-Litterman model says with a known risk free rate and covariance matrix we can compute the stock returns used. We load the data. 
```{r}
#| warning: false
rm(list=ls(all=TRUE))
library(ggplot2)
library(dplyr)
library(rjags)
library(tidybayes)
library(xts)
library(SharpeR)# data
library(gridExtra)

data(stock_returns)
r<-stock_returns
head(r)
N=nrow(r)
K=4
```

Use rJAGS to get posterior distributions of the returns.
```{r}
set.seed(123)

model_code <- "
model {
  #likelihood
  for (i in 1:N) {
    y[i,] ~ dmnorm(mu, Sigma_Inv)
  }

  # Prior on mean vector
  for(k in 1:K) {
    mu[k]~dnorm(0, 1 /100 ^ 2)
  }

  # Prior on covariance matrix
  Sigma_Inv ~ dwish(I, K+1)
}
"
data_list <- list(
  N = N,
  K=K,
  I = diag(K),
  y=r
)
model <- jags.model(textConnection(model_code), 
                    data=data_list, 
                    n.chains = 5);
update(model, 1000, progress.bar = "none"); # Burnin for 1000 samples

posterior_sample <- coda.samples(model, 
                                 variable.names = c("mu","Sigma_Inv"),
                                 n.iter = 10, progress.bar = "none")

#summary(posterior_sample)

mu_dat <-         posterior_sample %>% spread_draws(mu[i]|i)#tidybayes
Sigma_Inv_dat <- posterior_sample %>%  tidy_draws(Sigma_Inv)#tidybayes
```
Let $x$ be the portfolio vector, $r_x$ be portfolio return, $r_f$ be risk-free-rate, $S$ be covariance matrix of the stock returns. We have:
$$\lambda=\frac{r_x-r_f}{x^TSx}$$
Let $r$ be computed stock returns:
$$r=\lambda Sx+r_f$$
```{r}
#Black-Litterman Model
S=cov(r)
risk.free.rate=.01 #risk free rate
port=c(0.20247656,  0.26518714, 0.3566089,  0.17572744)#envelope portfolio
port.r=0.01016 #portfolio reurn
var_port=port%*%S%*%port
lambda=as.numeric((port.r-risk.free.rate)/var_port)
implied.r=lambda*S%*%port+risk.free.rate
implied.r
```
We plot computed returns against posterior return distributions. We can see the computed returns are very far away from posterior return distributions. We can conclude to get such high return from the stocks was not plausible. 
```{r}
#posterior predictive plot

posterior_ret <- rename_with(mu_dat, function(x) paste0("Posterior_return_", x))#dplyr
names(posterior_ret)

# Density curves
p1<-ggplot(posterior_ret, aes(x=Posterior_return_1)) + geom_density(alpha=.5)+
    geom_vline(aes(xintercept=mean(implied.r[1,1], na.rm=T)),   
               color="red", linetype="dashed", size=1)
p2<-ggplot(posterior_ret, aes(x=Posterior_return_2)) + geom_density(alpha=.5)+
    geom_vline(aes(xintercept=mean(implied.r[1,1], na.rm=T)),   
               color="red", linetype="dashed", size=1)
p3<-ggplot(posterior_ret, aes(x=Posterior_return_3)) + geom_density(alpha=.5)+
    geom_vline(aes(xintercept=mean(implied.r[1,1], na.rm=T)),   
               color="red", linetype="dashed", size=1)
p4<-ggplot(posterior_ret, aes(x=Posterior_return_4)) + geom_density(alpha=.5)+
    geom_vline(aes(xintercept=mean(implied.r[1,1], na.rm=T)),   
               color="red", linetype="dashed", size=1)

grid.arrange(p1, p2, p3, p4, ncol = 2)
```