---
title: "Bayesian Optimization Pairs Trading"
---

https://zorro-project.com/manual/en/Lecture%204.htm

Pairs trading, hedge ratio we knew them, no need to repeat anything. Again I adopted codes from link above. You may want to read it from there. For pairs trading we need an upper bond and a lower bond to mark entry points for placing orders, the bonds can be computed as $mean \pm sdtv$. In this material we have optimized bonds are $(-0.02238346,  8.56827139)$. Let's make a plot with the optimized bonds @fig-pd1.

```{r}
#| warning: false
require(quantmod)
require(PerformanceAnalytics)
require(rBayesianOptimization)


rm(list=ls(all=TRUE))
set.seed(4587)
setwd("C:\\tuDrive2026\\Bayesian-Financial-Portfolio-Analysis-in-R\\")
BBBB<-read.csv("BBBB.csv")
QQQQ<-read.csv("QQQQ.csv")

mydata<-merge(BBBB,QQQQ,by="Index")
mydata[1:6,]

 BB   <- mydata$X601857.Close
 QQ   <- mydata$X601318.Close
 
 #define training set
 rangeT  <-mydata[,1]
 BB   <- as.ts(BB)
 QQ   <- as.ts(QQ)

#compute price differences on in-sample data
 pdBB <- diff(BB)[-1]
 pdQQ <- diff(QQ)[-1]
 
 #build the model
 model  <- lm(pdBB ~ pdQQ - 1)

 #extract the hedge ratio
 hr     <- as.numeric(model$coefficients[1])

#spread price (in-sample)
 spreadT <- BB - hr * QQ
 
 #compute statistics of the spread
 meanT    <- as.numeric(mean(spreadT,na.rm=TRUE))
 sdT      <- as.numeric(sd(spreadT,na.rm=TRUE))
 upperThr <- 8.56827139
 lowerThr <- -0.02238346
 
```
```{r}
#| label: fig-pd1
#| fig-cap: "Plot upper and lower thresholds with residual series."
 #visualize the in-sample spread + stats
 plot(spreadT, main = "AAPL vs. QQQ spread (in-sample period)")
 abline(h = meanT, col = "red", lwd =2)
 abline(h = upperThr, col = "blue", lwd=2)
 abline(h = lowerThr, col = "blue", lwd=2)

```
The code below shows to buy and sell with the thresholds and the residual series @fig-pd2. The logic is nice and clear, no need to say much about it.
```{r}
#| label: fig-pd2
#| fig-cap: "Two order entry points red and green"
indSell <- which(spreadT >= upperThr)
indBuy  <- which(spreadT <= lowerThr)

 spreadL  <- length(spreadT)
 pricesB  <- c(rep(NA,spreadL))
 pricesS  <- c(rep(NA,spreadL))
 sp       <- as.numeric(spreadT)
 tradeQty <- 100
 totalP   <- 0
 holding.pos<-length(spreadT)

 for(i in 1:spreadL) {
     spTemp <- sp[i]
     if(spTemp < lowerThr) {
        if(totalP <= 0){ #have some to buy
           totalP     <- totalP + tradeQty
           pricesB[i] <- spTemp
        }
     } else if(spTemp > upperThr) {
       if(totalP >= 0){ #have some to sell
          totalP <- totalP - tradeQty
          pricesS[i] <- spTemp
       }
    }
  holding.pos[i]<-totalP
 }


 plot(spreadT, main = "BBBB vs. QQQQ spread (in-sample period)")
 abline(h = meanT, col = "red", lwd =2)
 abline(h = upperThr, col = "blue", lwd = 2)
 abline(h = lowerThr, col = "blue", lwd = 2)
 points(as.ts(pricesB,index(spreadT)), col="green", cex=1.9, pch=19)#buy
 points(as.ts(pricesS,index(spreadT)), col="red", cex=1.9, pch=19)#sell


spReturns = diff(sp)/tail(sp,-1)#lagged
trading.sign=sign(tail(holding.pos,-1))#lagged

trading.return=trading.sign*spReturns 
sum(trading.return)

SharpeRatio(as.ts(trading.return), Rf=.035/252, FUN="StdDev") #252 tradings a year
#cbind(tail(holding.pos,-1),spReturns )
```

After we can place orders, we can compute return series of the orders, also use Sharpe ratio to evaluate the return series. The upper lower thresholds which produce the best Sharpe ratio for our residuals series are the best thresholds. Optimization method we using here is Bayesian optimization. The end result is what we used for plotting.    
```{r}
opt_thresholds <- function(lower, upper) {
 lowerThr=lower
 upperThr=upper
 spreadL  <- length(spreadT)

 sp       <- as.numeric(spreadT)
 tradeQty <- 100
 totalP   <- 0
 holding.pos<-length(spreadT)

 for(i in 1:spreadL) {
     spTemp <- sp[i]
     if(spTemp < lowerThr) {
        if(totalP <= 0){ #have some to buy
           totalP     <- totalP + tradeQty
            }
     } else if(spTemp > upperThr) {
       if(totalP >= 0){ #have some to sell
          totalP <- totalP - tradeQty
           }
    }
  holding.pos[i]<-totalP
 }
spReturns = diff(sp)/tail(sp,-1)#lagged
trading.sign=sign(tail(holding.pos,-1))#lagged

trading.return=trading.sign*spReturns 

sr=SharpeRatio(as.ts(trading.return), Rf=.035/252, FUN="StdDev") #252 tradings a year
return(list(Score = as.numeric(sr[,1])))# returns a score list

}

# Bayesian Optimization
optimizer <- BayesianOptimization(
  FUN = opt_thresholds,
  bounds = list(lower = c(-2, 0), upper = c(.01, 19)),
  init_points = 10,
  n_iter = 10,
  acq = "ucb",
  verbose = TRUE
)

cat("Optimal thresholds:\n")
print(optimizer$Best_Par)
```