---
title: "Bayesian Market Maker"
---
https://github.com/mmargenot/machine-learning-market-maker/

I adopted this code from link above. At first we need to define some global variables, define how to get prices and volatility. Price distribution and prices the market maker produced are declared as vectors. 
```{r}

# Load required libraries
#library(ggplot2)
#library(quantmod)
#library(dplyr)

#self.setSymbol <- StockTicker
setAlpha <- .05
setNoise <- 3


#Get initial price (placeholder)
getInitialPrice = function() {
 #Check google finance and get current price
 return(100) # placeholder value
}

# Get volatility (placeholder)
getVolatility = function() {
  # Check google finance and calculate volatility
  return(0.05) # placeholder value
}

# Initialize the distribution
Distribution <- list() # Distribution is a list with Price : Probability(Price)
TruePrice <- c()
```

Compute the global variables to get initialized. 
```{r}

V0 <- getInitialPrice() # Checks google finance and gets price
vol <- getVolatility() # Calculates volatility from google finance

Vmin <- V0 - 4 * vol * V0
Vmax <- V0 + 4 * vol * V0 - 0.01

V <- 0
i <- 0
while((Vmin + i) <= Vmax) {
  V <- Vmin + i
  Distribution[[round(V, 2)]] <- pnorm(-4 * vol * V0 + i + 0.01, 0, vol * V0) - pnorm(-4 * vol * V0 + i, 0, vol * V0)

  i <- i + 0.01
}

Pb <- V0 - vol * V0 * 0.5
Pa <- V0 + vol * V0 * 0.5

TruePrice <- c(TruePrice, V0)
```

Now put to work. Every time it received an order, it will update price distribution and bid/ask prices. Market making is all about give price for trading.  
```{r}
# Update the probability densities
updateDensity = function(OrderSide) {
  if (OrderSide == "SELL") {
    for (price in names(Distribution)) {
      if (as.numeric(price) <= Pb) {
        post <- (1 - setAlpha) * 0.5 + setAlpha * pnorm(Pb - as.numeric(price), 0, setNoise * V0)
        Distribution[[price]] <- post * Distribution[[price]] / 0.5
          } else {
        post <- (1 - setAlpha) * 0.5 + setAlpha * (1 - pnorm(as.numeric(price) - Pb, 0, setNoise * V0))
        Distribution[[price]] <- post * Distribution[[price]] / 0.5
          }
        }
      } else {
    for (price in names(Distribution)) {
          if (as.numeric(price) <= Pa) {
        post <- (1 - setAlpha) * 0.5 + setAlpha * (1 - pnorm(Pa - as.numeric(price), 0, setNoise * V0))
        Distribution[[price]] <- post * Distribution[[price]] / 0.5
          }
        }
      }
    }
#updateDensity("SELL") 

# Update the bid-ask spread
updateSpread = function() {
  cumSum1 <- 0
  cumSum2 <- 0

  for (price in names(Distribution)) {
    if (as.numeric(price) <= Pb) {
      a <- Pb - as.numeric(price)
      cumSum1 <- cumSum1 + (0.5 - 0.5 * setAlpha + setAlpha * pnorm(a, 0, setNoise * V0)) *
        Distribution[[price]] * as.numeric(price)
    } else {
      a <- as.numeric(price) - Pb
      cumSum2 <- cumSum2 + (0.5 - 0.5 * setAlpha + setAlpha * (1 - pnorm(a, 0, setNoise * V0))) *
        Distribution[[price]] * as.numeric(price)
    }
  }

  newPb <- 2 * (cumSum1 + cumSum2)

  cumSum1 <- 0
  cumSum2 <- 0

  for (price in names(Distribution)) {
    if (as.numeric(price) <= Pa) {
      a <- Pa - as.numeric(price)
      cumSum1 <- cumSum1 + (0.5 - 0.5 * setAlpha + setAlpha * (1 - pnorm(a, 0, setNoise * V0))) *
          Distribution[[price]] * as.numeric(price)
      } else {
        a <- as.numeric(price) - Pa
        cumSum2 <- cumSum2 + (0.5 - 0.5 * setAlpha + setAlpha * pnorm(a, 0, setNoise * V0)) *
          Distribution[[price]] * as.numeric(price)
      }
    }

  newPa <- 2 * (cumSum1 + cumSum2)
  Pb <- newPb
  Pa <- newPa

  TruePrice <- c(TruePrice, (Pa + Pb)/2) # Add the true price to our list
  return(list(Pa, Pb)) # Returns Pa and Pb so that we can input the new orders
}

 
```

How about include other price series, like price from competitors, as a calibration into computation. The code is just a workflow, we can use other Bayesian estimators for the distribution and many other things.
